\Large Analyzing the Supreme Court Citation Network

### 2017-12-22 Tex/paper.tex
reviewing past work on citaitons

@@

>>>>

We are not the first to study what predicts citations on the Supreme Court...

We are the first to examine at the level of the citation, and, as a result, be able to incorporate complex dependence into our explanation of citations.

@@

\begin{itemize}

\item \citet{clark2010locating} Estimates a latent coordinate model of supreme court opinions based on the network of supreme court citations. Find that the majority opinion falls at the ideal point of the median member of the majority coalition. Account for negative citations. WE COULD USE THIS DATASET AS A SECOND APPLICATION

\item \citet{cross2010determinants} Look at the total number of citations to Supreme Court opinions over a ten year period of the Rehnquist Court. (case level).  Found case issue area, opinion ideology, opinion author, vote margin was not significant. Negative citations decreased future positive citations.

\item \citet{black2013citation} Study the number of citations to a case over time, in order to understand the lifecycle of citation rates.  Show that the rate of citations to a case goes down very quickly. THE EFFECT OF AN INDEPENDENT VARIABLE ON A PRECEDENT IS DEPENDENT UPON THE AGE OF THE CASE.

\item \citet{benjamin2012standing} Study the propensity for cases to be overruled and cited in other negative ways. They find that cases with large and broad majorities rare less likely to be cited negatively.

\item \citet{spriggs2001explaining} Find that cases are more likely to be overruled when the Court is ideologically distant from the median justice in the majority coalition that decided the case, when the legal issues under consideration are complex, whn the cases ha been negatively treated previously, when there were many concurring opinions, and less likely to be overruled if it was a unanimous coalition.

\item \citet{lupu2013strategic} The hub score, which is a measure of the degree to which a case cites other important cases increases with salience [GET THE AMICUS BRIEFS, NYT COUNTS]. Lower if stautory cases. Increases with ideological variance of the majority coalition.  Increases with the number of concurring opinions.
